New approaches for boosting to uniformity

### 2014-09-09 assets/paperdraft/paper_draft.tex
Mike edits

\title{New Approaches to Uniform Boosting}

\author{
Aleksandar Bukva, 
Vladimir Gligorov$^d$,
Alex Rogozhnikov$^{a,b}$\thanks{Corresponding author.}~ ,
Andrey Ustuzhanin$^b$ and
Mike Williams$^c$\\
\llap{$^a$}Lomonosov Moscow State University, Moscow, Russia\\
\llap{$^b$}Yandex LLC, Moscow, Russia\\
\llap{$^c$}Massachusetts Institute of Technology, Cambridge, MA, United States \\
\llap{$^d$}Organisation Europ\'eenne pour la Recherche Nucl\'eaire (CERN), Geneva, Switzerland  \\
E-mail: \email{alex.rogozhnikov@yandex.ru}}

@@

% AMS packages:
\usepackage{amsmath, amsthm, amsfonts}

@@

@@

\section{Uniformity Measurement}

\input{parts/metrics}

\section{Approaches Proposed}

\input{parts/approaches}

\section{Dataset}

\input{parts/dataset}

\section{Plots}

\input{parts/plots}

@@

@@

% The examples of items:
% \bibitem{bib1}
% Authors,
% \emph{Title},
% \emph{J. Ref.} \textbf{vol} (year) page.

% \bibitem{bib2}
% A. Pietropaolo et al., \emph{DINS measurements on VESUVIO in the
%     resonance detector configuration: proton mean kinetic energy in
%     water}, \jinst{1}{2006}{P04001}.

% \bibitem{bib3}
% A.I. Harris,
% \emph{Spectroscopy with multichannel correlation radiometers},
% \href{http://dx.doi.org/10.1063/1.1898643}
% {\emph{Rev.\ Sci.\ Instrum.} {\bf 76} (2005) 054503}
% [\astroph{0504449}].

% \bibitem{bib4}
% G.F. Knoll, \emph{Radiation detection and measurements}, John Wiley
%     and Sons, Inc., New York 2000.

% \bibitem{bib5}
% V. Dangendorf, \emph{Time-resolved fast-neutron imaging with a
% pulse-counting image intensifier}, in proceedings of
% \emph{International workshop on fast neutron detectors and
% applications}, April, 3--6, 2006 University of Cape Town, South Africa
% \pos{PoS(FNDA2006)008}.

@@

>>>>

\title{New approaches for boosting to uniformity}

\author{
Aleksandar Bukva$^{\rm ADD}$, 
Vladimir Gligorov$^d$,
Alex Rogozhnikov$^{a,b}$\thanks{Corresponding author.}~ ,
Andrey Ustuzhanin$^b$ and
Mike Williams$^c$\\
\llap{$^a$}Lomonosov Moscow State University, Moscow, Russia\\
\llap{$^b$}Yandex LLC, Moscow, Russia\\
\llap{$^c$}Massachusetts Institute of Technology, Cambridge, MA, United States \\
\llap{$^d$}Organisation Europ\'eenne pour la Recherche Nucl\'eaire (CERN), Geneva, Switzerland  \\
E-mail: \email{alex.rogozhnikov@yandex.ru}}

@@

% AMS packages:
\usepackage{amsmath, amsthm, amsfonts, xspace}

@@

\def \x {\ensuremath{\vec{x}}\xspace}
\def \y {\ensuremath{\vec{y}}\xspace}
\def\knn{\text{knn}}
\def\knni{\text{knn}(i)}

@@

%\section{Uniformity Measurement}
%\input{parts/metrics}
%\section{Approaches Proposed}
%\input{parts/approaches}

\section{Uniformity Boosting Methods}
\input{parts/methods}

\section{Example Analysis}

\input{parts/dataset}
\input{parts/plots}

@@

%\textcolor{red}{xxx}

@@

\bibitem{ref:lhcbhlt} R. Aaij {\em et al.} [LHCb Trigger Group], {\em The LHCb trigger and its performance}, JINST {\bf 8}, P04022 (2013). [arXiv:1211.3055]

\bibitem{ref:bbdt}  V. Gligorov and M. Williams, {\em Efficient, reliable and fast high-level triggering using a bonsai boosted decision tree}, JINST {\bf 8}, P02013 (2013). [arXiv:1210.6861]

\bibitem{ref:uboost} J. Stevens and M. Williams, {\em uBoost: A boosting method for producing uniform selection efficiencies from multivariate classifiers}, JINST {\bf 8}, P12013 (2013) [arXiv:1305.7248]

@@

\appendix
\section{Other Flatness Loss Criteria}

ADD THEIL, ETC DESCRIPTIONS AND HOW TO IMPLEMENT IN THE ALGORITHM HERE.
